### 2016-11-03 thesis/intro/intro.tex
tmp commit

\subsection{Causes of Obesity}
\label{sub:causes_of_obesity}

Obesity is caused by continuous intake of excessive energy without expending the energy gained.
As one can suspect, there are many factors involved with the likelihood of an individual to become overweight and obese.

@@

There are many environmental factors associated with the global rise in obesity (discussed in \cref{ssub:Population-level_(macro-level)_factors}: \nameref{ssub:Population-level_(macro-level)_factors}).
Even though these environmental factors are probably the most significant contributor of global obesity epidemic, there are some individual-level, genetic factors that assist in the overall increase in the obese population.

@@

\citep{Neel1962}

@@

>>>>

\subsection{Physiological mechanism of obesity}
\label{sub:physiological_mechanism_of_obesity}

Obesity is caused by continuous intake of food, whether they are controlled or not, without expending all of the energy gained.
The key to the problem is the control of food intake and energy expenditure, and how they are regulated in your body.

\subsubsection{Role of hypothalamus and arcuate nucleus in food intake control}
\label{ssub:role_of_hypothalamus_and_arcuate_nucleus_in_food_intake_control}

The central role of hypothalamus in the context of obesity is the control of satiety, and therefore food intake.
The hypothalamus receives both nueronal and hormonal inputs from the body and propagates the signal to the downstream neurons that ultimately affect the food intake of the individual \citep{Bell2005, Spiegelman2001}.

Within the hypothalamus, there is a group of neurons located within the arcuate nucleus that is essential for satiety signal transmission.
There are two types of neurons in the arcuate nucleus: orexogenic and anorexogenic neurons.
Orexogenic neurons are responsible for the promotion of food intake and reducing energy expenditure, whereas the anorexogenic neurons have the opposite effect \citep{Barsh2002}.

The orexogenic neurons produce \gls{npy} and \gls{agrp} which induces orexogenic signal to the downstream neurons; anorexogenic neurons produce \gls{pomc} and \gls{cart} which induces anorexogenic signal to the downstream neurons \citep{Barsh2002, Spiegelman2001}.
When stimulated by, for example, endocrine signals, these two different types of neurons act on the downstream neurons to promote or reduce food intake and energy expenditure.

\subsubsection{Role of hormones on arcuate nucleus neurons}
\label{ssub:role_of_hormones_on_arcuate_nucleus_neurons}

\subsection{Factors that affect the prevalence of obesity}
\label{sub:factors_that_affect_the_prevalence_of_obesity}

As one can suspect, there are many factors involved with the likelihood of an individual to become overweight and obese.

@@

There are many environmental factors associated with the global rise in obesity (discussed in \cref{ssub:Population-level_(macro-level)_factors}: \nameref{ssub:Population-level_(macro-level)_factors}).
Even though these environmental factors are probably the most significant contributor of the current global obesity epidemic, there are some individual-level, genetic factors that assist in the overall increase in the obese population.

@@

@@

Talk about all the mutations and contribution of these genes to obesity, and then link it back to ``thrifty'' gene
\citep{Neel1962}
